Aa Language Reference Manual

### 2017-02-12 v2/Ahir-asm/devel/docs/AaLRM.tex
A lacuna in WAR dependency handling.  closed.
Update LRM to mention $mark $synch $delay constructs.

Pipe variable declarations can also be appended by
the following keywords:
\begin{verbatim}
   ($in | $out)? ($signal)? 
\end{verbatim}
These additional keywords mean the following things:
\begin{itemize}
\item Inclusion of ``\$in'' (respectively ``\$out'') means
that the pipe is a read-only (respectively write-only) object.
\item The ``\$signal'' keyword means that the pipe behaves
like a variable.  That is, it remembers the last value
that was written to it.    
\end{itemize}
Pipe depths can be specified by parameters or parameter
expressions.
\item {\bf Constant} variables declared at
the program scope are globally visible and have
initial values which can never be altered in the program.
Thus, an assignment to a constant is an error.
A constant declaration has the form
\begin{verbatim}
$constant <constant-name>: <constant-type> := <initial-value>
\end{verbatim}
For example
\begin{verbatim}
$constant wordlength: $uint<32> := 16
\end{verbatim}
\item {\bf Implicit} or {\bf Static Single Assignment}
variables are created by statements in the \Aa program
(as described below in Section \ref{sec:Statements}).
These are analogous to registers that can be written
into only from one point,  but can be
read from several points in the program.
Implicit variables are not declared, but are defined
by the statements which write to them.
\end{itemize}

@@

>>>>

Pipe variable declarations can also be appended by
the following keywords:
\begin{verbatim}
   ($in | $out)? ($signal)? 
\end{verbatim}
These additional keywords mean the following things:
\begin{itemize}
\item Inclusion of ``\$in'' (respectively ``\$out'') means
that the pipe is a read-only (respectively write-only) object.
\item The ``\$signal'' keyword means that the pipe behaves
like a variable.  That is, it remembers the last value
that was written to it\footnote{    
Note that a read from a signal will block until the
signal has been written into at least once!}.
\end{itemize}
Pipe depths can be specified by parameters or parameter
expressions.
\item {\bf Constant} variables declared at
the program scope are globally visible and have
initial values which can never be altered in the program.
Thus, an assignment to a constant is an error.
A constant declaration has the form
\begin{verbatim}
$constant <constant-name>: <constant-type> := <initial-value>
\end{verbatim}
For example
\begin{verbatim}
$constant wordlength: $uint<32> := 16
\end{verbatim}
\item {\bf Implicit} or {\bf Static Single Assignment}
variables are created by statements in the \Aa program
(as described below in Section \ref{sec:Statements}).
These are analogous to registers that can be written
into only from one point,  but can be
read from several points in the program.
Implicit variables are not declared, but are defined
by the statements which write to them.
\end{itemize}

@@

Complete atomic statements can be explicitly sequenced using
the \$mark and \$synch constructs.  For example
\begin{verbatim}
a := (b + c) $mark FIRST
e := (f + g) $mark SECOND $synch (FIRST)
h := (i + j) $synch (FIRST SECOND)
\end{verbatim}
means that the second statement will be {\em started}
only after the first statement has {\em started}.  The
third statement will be started only after the first
two have started. This
is necessary in some cases where dependency analysis
says that two statements are independent, but you wish
to force explicit ordering.

A related construct is \$delay which explicitly sets
the delay between the completion of two statements
(which otherwise seem unrelated)
\begin{verbatim}
// from_pipe, to_pipe are pipes.
to_pipe := (a + b) $mark WPIPE
e := from_pipe  $delay (WPIPE 10)
\end{verbatim}
This says that there is delay of 10 units (clock cycles)
between the write to to\_pipe and the read from from\_pipe.
This delay information is used by the compiler to 
balance pipelines.
